MSD panels 1, 2 and 3 Explant Supernatant

### 2016-09-23 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
added scatter plots back to HVE file and edited plot titles in both files

>>>>

```{r scatter plots of mock subtracted, echo=FALSE,fig.width=8, fig.height = 15, message = FALSE, warning = FALSE}

ggplot(mergeMock, aes(x = Timepoint, y = logMockSubtracted))+
   geom_jitter(aes(color = Donor), alpha = 0.75, size = 2.5, width = 0.2, height = 0.2)+
  labs( y = "log 10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Mock Subtracted Analyte Concentrations ")
```

### 2016-09-23 MSD_panels_1_2_3_explant_sup_analysis.Rmd
added scatter plots back to HVE file and edited plot titles in both files

>>>>

```{r scatter plots of mocksubtracted, fig.width = 6,fig.height= 13, echo=FALSE}

ggplot(mergeMock, aes(x = Timepoint, y = logMockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "log 10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  #geom_hline(yintercept = 0)+
  ggtitle("Mock Subtracted Analyte Concentrations")

This is just donors 317,318,323 and 324, which were interesting in the microarray

```{r subset scatter plots, fig.width = 6,fig.height= 13, echo=FALSE}

#Make plots just showing data for donors 317, 318, 323,324

subset<-mergeMock%>%
  filter(Donor == "317"|Donor == "318"|Donor =="323"|Donor =="324")

#plot it

ggplot(subset, aes(x = Timepoint, y = logMockSubtracted))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
   labs( y = "log10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Mock Subtracted Analyte Concentrations")
```
